Stochastic Wind Power Forecasting

### 2020-05-17 LaTeX_Code/Paper/paper_1line.tex
Corrected most figures in paper

\begin{figure}[H]
\centering
\includegraphics[width=0.35\textwidth]{plots/5.eps}
\includegraphics[width=0.35\textwidth]{plots/245.eps}\\
\includegraphics[width=0.35\textwidth]{plots/661.eps}
\includegraphics[width=0.35\textwidth]{plots/805.eps}
\caption{Four 24-hour segments with the wind power real production in Uruguay (orange line) recorded every ten minutes, and the hourly wind power production forecasted by provider A (blu line).}
  \label{fig:sample_data}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.35\textwidth]{plots/LP_6.eps}
\includegraphics[width=0.35\textwidth]{plots/MP_6.eps}\\
\includegraphics[width=0.35\textwidth]{plots/HP_6.eps}
\includegraphics[width=0.35\textwidth]{plots/AP_6.eps}
\caption{Wind production forecast error histograms during the period April-December 2019: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
  \label{fig:data_curtailing}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.35\textwidth]{plots/LP.eps}
\includegraphics[width=0.35\textwidth]{plots/MP.eps}\\
\includegraphics[width=0.35\textwidth]{plots/HP.eps}
\includegraphics[width=0.35\textwidth]{plots/AP.eps}
\caption{Wind production forecast error histograms during the period April-December 2019 after removing 24-hour segments with artificial wind curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
  \label{fig:data_after_clean}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.35\textwidth]{plots/LP_t.eps}
\includegraphics[width=0.35\textwidth]{plots/MP_t.eps}\\
\includegraphics[width=0.35\textwidth]{plots/HP_t.eps}
\includegraphics[width=0.35\textwidth]{plots/AP_t.eps}
\caption{Forecast error transition histograms during the period April-December 2019 without wind power production curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
\label{fig:error_transitions}
\end{figure}

@@

\begin{figure}[h]
  %\includegraphics[width=26mm,scale=1]{}
  \caption{{\color{red} Add Figure showing the difference with and without derivative tracking}}
  \label{fig:derivative_tracking}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.35\textwidth]{plots/LP_t_LP.eps}
\includegraphics[width=0.35\textwidth]{plots/MP_t_LP.eps}\\
\includegraphics[width=0.35\textwidth]{plots/HP_t_LP.eps}
\includegraphics[width=0.35\textwidth]{plots/AP_t_LP.eps}
\caption{Transitions after the Lamperti transform. The transitions now present a normal Gaussian shape. This effect motivates the use of Gaussian proxies to approximate the process after using the Lamperti transform.}
  \label{fig:LP_transitions}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.18\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/1.eps}
\includegraphics[width=0.18\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/2.eps}\\
\quad\\
\includegraphics[width=0.18\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/3.eps}
\includegraphics[width=0.18\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/4.eps}
\caption{Five simulated wind power production paths using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. }
\label{fig:simulation_paths}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.35\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/1.eps}
\includegraphics[width=0.35\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/2.eps}\\
\quad\\
\includegraphics[width=0.35\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/3.eps}
\includegraphics[width=0.35\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/4.eps}
\caption{Empirical pointwise confidence bands for the wind power production using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. Blue line: real production.}
\label{fig:confidence_bands}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/histograms/classic/Optimal.eps}
\includegraphics[width=0.48\textwidth]{../../MATLAB_Files/Results/histograms/classic/Lamperti_Optimal.eps}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{plots/four_days/377.eps}
\includegraphics[width=0.45\textwidth]{plots/four_days/417.eps}\\
\quad\\
\includegraphics[width=0.45\textwidth]{plots/four_days/437.eps}
\includegraphics[width=0.45\textwidth]{plots/four_days/477.eps}
\caption{Four 24-hour segments with the wind power real production in Uruguay (orange line) recorded every ten minutes, and the hourly wind power production forecasted by provider A (blu line).}
  \label{fig:sample_data}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{plots/LP_6.eps}
\includegraphics[width=0.45\textwidth]{plots/MP_6.eps}\\
\quad\\
\includegraphics[width=0.45\textwidth]{plots/HP_6.eps}
\includegraphics[width=0.45\textwidth]{plots/AP_6.eps}
\caption{Wind production forecast error histograms during the period April-December 2019: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
  \label{fig:data_curtailing}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{plots/LP.eps}
\includegraphics[width=0.45\textwidth]{plots/MP.eps}\\
\quad\\
\includegraphics[width=0.45\textwidth]{plots/HP.eps}
\includegraphics[width=0.45\textwidth]{plots/AP.eps}
\caption{Wind production forecast error histograms during the period April-December 2019 after removing 24-hour segments with artificial wind curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
  \label{fig:data_after_clean}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{plots/LP_t.eps}
\includegraphics[width=0.45\textwidth]{plots/MP_t.eps}\\
\quad\\
\includegraphics[width=0.45\textwidth]{plots/HP_t.eps}
\includegraphics[width=0.45\textwidth]{plots/AP_t.eps}
\caption{Forecast error transition histograms during the period April-December 2019 without wind power production curtailment: low-power (upper-left graph), mid-power (upper-right graph), high-power (lower-left graph), and the global range of power (lower-right graph).}
\label{fig:error_transitions}
\end{figure}

@@

\begin{figure}[h]
\centering
  \includegraphics[width=0.45\textwidth]{plots/31.eps}\includegraphics[width=0.45\textwidth]{plots/31_2.eps}
  \caption{{\color{red} Add Figure showing the difference with and without derivative tracking}}
  \label{fig:derivative_tracking}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{plots/LP_t_LP.eps}
\includegraphics[width=0.45\textwidth]{plots/MP_t_LP.eps}\\
\quad\\
\includegraphics[width=0.45\textwidth]{plots/HP_t_LP.eps}
\includegraphics[width=0.45\textwidth]{plots/AP_t_LP.eps}
\caption{Transitions after the Lamperti transform. The transitions now present a normal Gaussian shape. This effect motivates the use of Gaussian proxies to approximate the process after using the Lamperti transform.}
  \label{fig:LP_transitions}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/1.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/2.eps}\\
\quad\\
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/3.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/4.eps}
\caption{Five simulated wind power production paths using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. }
\label{fig:simulation_paths}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/1.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/2.eps}\\
\quad\\
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/3.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/bands_testing_days/optimal_value/withDate/4.eps}
\caption{Empirical pointwise confidence bands for the wind power production using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.2,0.1,0.6)$. Blue line: real production.}
\label{fig:confidence_bands}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/histograms/classic/Optimal.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/histograms/classic/Lamperti_Optimal.eps}
\end{figure}
